Artin Group Presentations of Reflection Groups

### 2014-07-17 Paper.tex
section labels and main thm to intro

\section{Introduction \& Motivation}\todo{let's add the statement of the main theorem to the introduction - David}

\todo{use section labels rather than explicit numbers}
In \cite{FZ02}, Fomin and Zelevinsky first introduced the concept of cluster algebras. This introductory paper focused on structural features of cluster algebras, specifically that, in a given cluster, when any cluster variable is viewed as a rational function in the variables of the given cluster, this cluster variable is a Laurent polynomial. Fomin and Zelevinsky initially defined this type of commutative ring in order to make further strides in the areas of representation theory, Lie theory, and total positivity. Since then, the study of cluster algebras has provided a motivation for applications in various other areas of mathematics, including quiver representations. Of particular interest were \textit{finite-type} cluster algebras; that is, cluster algebras whose variables are generated through mutation on a finite number of \textit{seeds}. In the 2003 sequel to their introductory paper (\cite{FZ03}), Fomin and Zelevinsky introduce the concept of \textit{mutation equivalence} between diagrams, proving that a connected graph is mutation equivalent to an oriented Dynkin diagram if and only if all mutation equivalent graphs have edge weights not exceeding 3. In particular, this proves that finite-type cluster algebras can be classified by Dynkin diagrams. \\
\indent Barot and Marsh extended Fomin and Zelevinsky's results in \cite{BM13}, providing a presentation of the reflection group associated to a Dynkin diagram with generators that correspond to elements of a companion basis associated to a seed of a finite-type cluster algebra. They also proved that this group presentation is invariant up to isomorphism under the mutation equivalence relation. That is, given a diagram $\Gamma$ and a diagram mutation equivalent to $\Gamma$, denoted $\Gamma^{\prime} = \mu_k(\Gamma)$, they proved that $W_{\Gamma} \cong W_{\Gamma^{\prime}}$, where $W_{\Gamma}$ and $W_{\Gamma^{\prime}}$ are the group representations corresponding to $\Gamma$ and $\Gamma^{\prime}$, respectively. \\
\indent Section 2 provides the necessary definitions and fundamental results from \cite{BM13} to provide motivation for our own results. For further definitions and references on the topic, we refer the reader to \cite{FZ02}. Section 3  will review theory from \cite{FZ02}, \cite{FZ03} as well as review the classifications (from \cite{BM13}) of mutations of diagrams and their oriented chordless cycles. In this section we also define the appropriate relations for our Artin group presentations. Section 4 specifies a relation for each case of the chordless cycles which suffices to show all the other relations in the group presentation hold. Finally, section \todo{for example}\ref{sec:proof_of_main} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$. \\

\section{Definitions and Notation}

@@

 A cluster algebra is said to be of \textit{finite type} if the number of cluster variables that generate it is finite (if it has finitely many seeds). For each finite type cluster algebra, we can associate to its corresponding skew-symmetrisable matrix an edge-weighted, oriented graph, called a \textit{diagram}. We will often denote this diagram by $\Gamma$, and the vertex set of $\Gamma$ by $\V$. We will denote two connected vertices by $i \rightarrow j$, or by $i\--\ j$ if the orientation is not specified. The diagram is determined by, for $i, j \in \V$, $i \xrightarrow{w} j$ if and only if $B_{ij} > 0$ and $w = |B{ij}B_{ji}|$ is the weight of the edge. A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B{ij}B_{ji}| \leq 3$ for $i, j \in {1, \ldots, n}$.  By \cite{FZ02}[7.5], we have that if $B$ is 2-finite, all 3-cycles in the unoriented graph underlying our diagram must be oriented cyclically. \\

Just as we can define mutations of the seeds of a cluster variable, we can also define mutations of a diagram associated to a cluster algebra by the following set of rules:
\begin{prop}\cite{BM13}[Proposition 1.4]
Let $B$ be a 2-finite skew-symmetrisable matrix. Then $\Gamma(\mu_k(B))$ is uniquely determined by $\Gamma(B)$ as follows: 
\begin{itemize}
\item Reverse the orientations of all edges in $\Gamma(B)$ incident with $k$ (leaving the weights unchanged)
\item For any path in $\Gamma(B)$ of form $i \xrightarrow{a} k \xrightarrow{b} j$ (i.e. with $a,b$ positive), let $c$ be the weight on the edge $j \rightarrow i$, taken to be zero if there is no such arrow. Let $c'$ be determined by $c'\geq 0$ and 
$c+c' =$ max$(a,b)$. 
Then $\Gamma(B)$ changes in a predetermined way, taking the case $c' = 0$ to mean no arrow between $i$ and $j$.
\end{itemize}
\end{prop}

@@

Using this group presentation, Barot and Marsh state the following result:
\begin{thm}\cite{BM13}[Theorem A]
Let $\Gamma$ be the diagram associated to a seed in a cluster algebra of finite type. Then $W(\Gamma)$ is isomorphic to the corresponding reflection group.
\end{thm}

@@

Defining the group $W_{\Gamma}$ with relations as shown above allows them to prove certain characteristics about the interaction between the relations in this group for the chordless cycles underlying the diagrams in question. In particular, they prove the following result, which we include as our main goal was to define analogous relations for an Artin group that would satisfy the same result.
\begin{thm}\cite{BM13}[Theorem 5.4a]
Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $W_{\Gamma} \cong W_{\Gamma^{\prime}}$.
\end{thm}

@@

\section{Diagrams of Finite Type}

In this section, we shall review the structure of diagrams of finite type, and how their cycles are effected by mutation. This section is simply a recap of \cite[Section 2]{BM13}.

@@

\section{The Group of a Diagram in an Artin Group}

@@

\section{Symmetry among (R3') Relations}

As in \cite{Barot}, given the relations (R2'), many of the relations in (R3')(a) and (b) become redundant. For example,

>>>>

\section{Introduction \& Motivation}
\label{sec:Intro}

In \cite{FZ02}, Fomin and Zelevinsky first introduced the concept of cluster algebras. This introductory paper focused on structural features of cluster algebras, specifically that, in a given cluster, when any cluster variable is viewed as a rational function in the variables of the given cluster, this cluster variable is a Laurent polynomial. Fomin and Zelevinsky initially defined this type of commutative ring in order to make further strides in the areas of representation theory, Lie theory, and total positivity. Since then, the study of cluster algebras has provided a motivation for applications in various other areas of mathematics, including quiver representations. Of particular interest were \textit{finite-type} cluster algebras; that is, cluster algebras whose variables are generated through mutation on a finite number of \textit{seeds}. In the 2003 sequel to their introductory paper (\cite{FZ03}), Fomin and Zelevinsky introduce the concept of \textit{mutation equivalence} between diagrams, proving that a connected graph is mutation equivalent to an oriented Dynkin diagram if and only if all mutation equivalent graphs have edge weights not exceeding 3. In particular, this proves that finite-type cluster algebras can be classified by Dynkin diagrams. \\
\indent Barot and Marsh extended Fomin and Zelevinsky's results in \cite{BM13}, providing a presentation of the reflection group associated to a Dynkin diagram with generators that correspond to elements of a companion basis associated to a seed of a finite-type cluster algebra. They also proved that this group presentation is invariant up to isomorphism under the mutation equivalence relation.

\begin{theorem}\cite[Theorem 5.4]{BM13}
\begin{enumerate}
\item Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $W_{\Gamma} \cong W_{\Gamma^{\prime}}$.
\item Let $\mathscr{A}$ be a cluster algebra of finite type. Then the groups $W_{\Gamma}$ associated to the diagrams $\Gamma$ arising from the seeds of $\mathscr{A}$ are all isomorphic (to the reflection group associated to the Dynkin diagram associated to $\mathscr{A}$).
\end{enumerate}
\end{theorem}

That is, given a diagram $\Gamma$ and a diagram mutation equivalent to $\Gamma$, denoted $\Gamma^{\prime} = \mu_k(\Gamma)$, they proved that $W_{\Gamma} \cong W_{\Gamma^{\prime}}$, where $W_{\Gamma}$ and $W_{\Gamma^{\prime}}$ are the group representations corresponding to $\Gamma$ and $\Gamma^{\prime}$, respectively. \\

\indent Section \ref{sec:main_definitions} provides the necessary definitions and fundamental results from \cite{BM13} to provide motivation for our own results. For further definitions and references on the topic, we refer the reader to \cite{FZ02}. Section \ref{sec:finite-type_diagrams}  will review theory from \cite{FZ02}, \cite{FZ03} as well as review the classifications (from \cite{BM13}) of mutations of diagrams and their oriented chordless cycles. In Section \ref{sec:defn_artingroup} we define the appropriate relations for our Artin group presentations. Section \ref{sec:one_relation} specifies a relation for each case of the chordless cycles which suffices to show all the other relations in the group presentation hold. Finally, Section \todo{for example}\ref{sec:proof_of_main} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$. \\

\section{Definitions and Notation}
\label{sec:main_definitions}

@@

 A cluster algebra is said to be of \textit{finite type} if the number of cluster variables that generate it is finite (if it has finitely many seeds). For each finite type cluster algebra, we can associate to its corresponding skew-symmetrisable matrix an edge-weighted, oriented graph, called a \textit{diagram}. We will often denote this diagram by $\Gamma$, and the vertex set of $\Gamma$ by $\V$. We will denote two connected vertices by $i \rightarrow j$, or by $i\--\ j$ if the orientation is not specified. The diagram is determined by, for $i, j \in \V$, $i \xrightarrow{w} j$ if and only if $B_{ij} > 0$ and $w = |B{ij}B_{ji}|$ is the weight of the edge. A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B{ij}B_{ji}| \leq 3$ for $i, j \in {1, \ldots, n}$.  By \cite[7.5]{FZ02}, we have that if $B$ is 2-finite, all 3-cycles in the unoriented graph underlying our diagram must be oriented cyclically. \\

Just as we can define mutations of the seeds of a cluster variable, we can also define mutations of a diagram associated to a cluster algebra by the following set of rules:
\begin{prop}\cite[Proposition 1.4]{BM13}
Let $B$ be a 2-finite skew-symmetrisable matrix. Then $\Gamma(\mu_k(B))$ is uniquely determined by $\Gamma(B)$ as follows: 
\begin{itemize}
\item Reverse the orientations of all edges in $\Gamma(B)$ incident with $k$ (leaving the weights unchanged)
\item For any path in $\Gamma(B)$ of form $i \xrightarrow{a} k \xrightarrow{b} j$ (i.e. with $a,b$ positive), let $c$ be the weight on the edge $j \rightarrow i$, taken to be zero if there is no such arrow. Let $c'$ be determined by $c'\geq 0$ and 
$c+c' =$ max$(a,b)$. 
Then $\Gamma(B)$ changes in a predetermined way, taking the case $c' = 0$ to mean no arrow between $i$ and $j$.
\end{itemize}
\end{prop}

@@

Using this group presentation, Barot and Marsh state the following result:
\begin{thm}\cite[Theorem A]{BM13}
Let $\Gamma$ be the diagram associated to a seed in a cluster algebra of finite type. Then $W(\Gamma)$ is isomorphic to the corresponding reflection group.
\end{thm}

@@

Defining the group $W_{\Gamma}$ with relations as shown above allows them to prove certain characteristics about the interaction between the relations in this group for the chordless cycles underlying the diagrams in question. In particular, they prove the following result, which we include as our main goal was to define analogous relations for an Artin group that would satisfy the same result.
\begin{thm}\cite[Theorem 5.4a]{BM13}
Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $W_{\Gamma} \cong W_{\Gamma^{\prime}}$.
\end{thm}

@@

\section{Diagrams of Finite Type}
\label{sec:finite-type_diagrams}

In this section, we shall review the structure of diagrams of finite type, and how their cycles are affected by mutation. This section is simply a recap of \cite[Section 2]{BM13}.

@@

\section{The Group of a Diagram in an Artin Group}
\label{sec:defn_artingroup}

@@

\section{Symmetry among (R3') Relations}
\label{sec:one_relation}

As in \cite{BM13}, given the relations (R2'), many of the relations in (R3')(a) and (b) become redundant. For example,
